Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-01-17 manuscripts/paper-1/main.tex

\documentclass[9pt,conference]{IEEEtran}
\usepackage{listings}
\usepackage{graphicx}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\graphicspath{{./images/}}

@@

    \section{Introduction}\label{section:introduction}

    Cyber-physical system (CPS), is a conceptual architecture/approach which aims to conjoin the physical and virtual space tightly. 
    The CPS aims to integrate communication and computing capabilities to physical entities to monitor, coordinate and control the physical space (where the physical assets exist) from the virtual space (where the virtual models exist) while achieving seamless, real-time connection between the spaces.
    The Digital twin approach, on the other hand, is a pragmatic solution, which is the execution of the CPS idea.~\cite{TAOCHAPTER1}

@@

    %TODO: How we are writing this?
    \subsection{Research objectives}

    Find an approach to assess the quality of Digital twins

    \subsection{Research questions}~\label{section: Research Questions}

    What is the quality of digital twins? 
    What is good quality?
    What is bad quality? 
    What is the impact of good quality? 
    What is the impact of bad quality? W
    What are typical quality issues? 
    How to assess quality?

    \subsection{Scientific contributions}

    Literature review (see Section~\ref{section: literature}), case study (see Section~\ref{section: Research Questions})...

    \section{Literature review}~\label{section: literature}
    Literature analysis was executed, to analyze current DT literature within the concept of digital twin quality. The analysis especially focused on 
    how the digital twin quality is mentioned and assessed within the academic dissertations.

    Methodology (see Section~\ref{section:liteature_methodology}), Result (see Section~\ref{section:liteature_result}), and Summary (See Section~\ref{section:liteature_summary})...
    \subsection{Methodology}~\label{section:liteature_methodology}
    Google Scholar (GS), Scopus (SCP) and Research Rabbit (RR) tools are used to fulfill our requirements for the literature review. 
    Since there is a great number of digital twin publications in academics, 
    narrowing the research is necessary, so the following algorithm which can be seen in Figure \ref{fig:literaturesearchalgorithm} with several levels of filtering will be applied.

@@

    Second filtering will be done to eliminate the duplications and even though authors already filtered the search for the English language,
    still some results without the English language will appear. Again, language filtering should be done to clean the results.

    \begin{itemize}
        \item Remove Duplications
        \item Remove the dissertations which are not English manually
    \end{itemize}

@@

    \subsection{Result}~\label{section:liteature_result}
    The following results were achieved by selecting several search terms.
    \subsubsection*{Digital Twin Quality}\label{subsection:DigitalTwinQuality}

    First filtering was done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results.
    After the second filtering process, 3 duplications and 31 different results were found. 10 dissertations were not in English.
    After the third filtering process, 9 dissertations passed and the rest is rejected.

    \subsubsection*{Digital Twin Model Verification}\label{subsection:DigitalTwinVerification}

    \subsubsection*{Digital Twin Model Validation}\label{subsection:DigitalTwinValidation}
    %What is the existing literature?

    \subsection{Summary}~\label{section:liteature_summary}

    What do we learn from existing literature?

@@

    \section{Case study (FELICE)}~\label{section:case}

    TODO (Explain the limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)

    \subsection{Methodology}~\label{section:case_methodology}

    TODO

    \subsection{Result}~\label{section:case_result}

    TODO

    \subsection{Summary}~\label{section:case_summary}

    TODO

>>>>

\documentclass[9pt,conference]{IEEEtran}

\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{amsfonts}
\graphicspath{{./images/}}

@@

    \section{Introduction}\label{section:introduction}
    Cyber-physical system (CPS), is a conceptual architecture/approach which aims to conjoin the physical and virtual space tightly. 
    The CPS aims to integrate communication and computing capabilities to physical entities to monitor, coordinate and control the physical space (where the physical assets exist) from the virtual space (where the virtual models exist) while achieving seamless, real-time connection between the spaces.
    The Digital twin approach, on the other hand, is a pragmatic solution, which is the execution of the CPS idea.~\cite{TAOCHAPTER1}

@@

    %TODO: How we are writing this?
    \subsection{Research objectives}
    Find an approach to assess the quality of Digital twins

    \subsection{Research questions}
    \label{section: Research Questions}
    What is a digital twin?
    What is the quality of digital twins? 
    What is good quality?
    What is bad quality? 
    What is the impact of good quality? 
    What is the impact of bad quality? W
    What are typical quality issues? 
    How to assess quality?

    \subsection{Scientific contributions}
    Literature review (see Section~\ref{section: literature}), case study (see Section~\ref{section: Research Questions})...

    \section{Literature review}
    \label{section: literature}
    Literature analysis was executed, to analyze current DT literature within the concept of digital twin quality. The analysis especially focused on 
    how the digital twin quality is mentioned and assessed within the academic dissertations.

    Methodology (see Section~\ref{section:liteature_methodology}), Result (see Section~\ref{section:liteature_result}), and Summary (See Section~\ref{section:liteature_summary})...

    \subsection{Methodology}
    \label{section:liteature_methodology}
    Google Scholar (GS), Scopus (SCP) and Research Rabbit (RR) tools are used to fulfill our requirements for the literature review. 
    Since there is a great number of digital twin publications in academics, 
    narrowing the research is necessary, so the following algorithm which can be seen in Figure \ref{fig:literaturesearchalgorithm} with several levels of filtering will be applied.

@@

    Second filtering will be done to eliminate the duplications and even though authors already filtered the search for the English language,
    still some results without the English language will appear. Again, language filtering should be done to clean the results.
    \begin{itemize}
        \item Remove Duplications
        \item Remove the dissertations which are not English manually
    \end{itemize}

@@

    \subsection{Result}
    \label{section:liteature_result}
    The following results were achieved by selecting several search terms.

    \subsubsection*{Digital Twin Quality}
    \label{subsection:DigitalTwinQuality}
    First filtering was done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results.
    After the second filtering process, 3 duplications and 31 different results were found. 10 dissertations were not in English.
    After the third filtering process, 9 dissertations passed and the rest is rejected.

    \subsubsection*{Digital Twin Model Verification}
    \label{subsection:DigitalTwinVerification}

    \subsubsection*{Digital Twin Model Validation}
    \label{subsection:DigitalTwinValidation}
    %What is the existing literature?

    \subsection{Summary}~\label{section:liteature_summary}
    What do we learn from existing literature?

@@

    \section{Digital twin framework}
    \label{section:framework_1}
    TODO

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{Digital Twin.png}
        \caption{TODO}
        \label{todo}
    \end{figure}

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{Digital Twin Deviation.png}
        \caption{TODO}
        \label{todo}
    \end{figure}

    \begin{figure}[htbp]
        \includegraphics[width=\columnwidth]{Continuous Quality Control.png}
        \caption{TODO}
        \label{todo}
    \end{figure}

    \subsection{Real system}
    TODO

    \subsubsection{Real state (RS)}
    TODO

    \subsubsection{Real state history (RSH)}
    TODO
    \[
        RSH: \mathbb{R} \rightarrow RS
    \]

    \subsubsection{Real state transition function (RSTF)}
    TODO
    \[
        RSTF: RS \rightarrow RS
    \]

    \subsubsection{Real state prediction (RSP)}
    TODO

    \subsection{Digital twin}
    TODO

    \subsubsection{Digital state (DS)}
    TODO

    \subsubsection{Digital state history (DSH)}
    In our digital world we cannot represent the continuous time domain of the real system completely.
    Instead, we have to discretize the time domain and sample the state history function.
    \[
        RSH: \mathbb{N} \rightarrow RS
    \]

    \subsubsection{Digital state transition function (DSTF)}
    Since we do not have perfect knowledge about real state and real state transition function, our simulation models typically are non-deterministic or probabilistic.
    Here we take a probabilistic viewpoint.
    \[
        DSRF: DS \rightarrow \mathbb{P}(DS)
    \]

    \subsubsection{Digital state prediction (DSP)}
    TODO

    \section{Digital twin quality framework}
    \label{section:framework_2}
    TODO

    \section{Case study (FELICE)}
    \label{section:case}
    TODO (Explain the limitations of the FELICE digital twin! It is not a complete digital twin according to literature! It includes this, it is missing this.)

    \subsection{Methodology}~\label{section:case_methodology}
    TODO

    \subsection{Result}~\label{section:case_result}
    TODO

    \subsection{Summary}~\label{section:case_summary}
    TODO
